### 2023-09-22 chapters/introduction.tex
Update

In practice, we are interested in the predictive uncertainty, so we need to include both aleatoric and epistemic parts in the uncertainty estimate. 
Since sources of epistemic uncertainty are by definition those not represented in the data, it is not generally possible to model them directly, as it is for aleatoric uncertainty. This makes epistemic uncertainty more difficult to model and quantify than aleatoric uncertainty. 
% Methods for estimating epistemic uncertainty include Bayesian neural networks \cite{mackay_practical_1992, neal_bayesian_1995}, ensembling \cite{gal_dropout_2016,lakshminarayanan_simple_2017} and a suite of recent research into out-of-distribution detection (see \cref{sec:out-of-distribution-detection}). 
In contrast to aleatoric uncertainty, which is usually represented by a distribution over the data, epistemic uncertainty is often represented by an implicit or explicit distribution over the model parameters, such as in Bayesian neural networks \cite{mackay_practical_1992, neal_bayesian_1995} and ensemble models \cite{gal_dropout_2016,lakshminarayanan_simple_2017}. In most cases, such methods require multiple forward passes through the model to estimate the predictive uncertainty making them computationally expensive and impractical for real-time applications. Within the field of out-of-distribution detection, the epistemic uncertainty is not always expressed in model parameters, but sometimes by a distribution over data representations, or output probabilities with special classes for out-of-distribution data. In such cases, the uncertainty can be estimated in a single forward pass through the model.

>>>>

In practice, we are interested in the predictive uncertainty, so we need to include both aleatoric and epistemic parts in the uncertainty estimate. 
Since sources of epistemic uncertainty are by definition those not represented in the data, it is not generally possible to model them directly, as it is for aleatoric uncertainty. This makes epistemic uncertainty more difficult to model and quantify than aleatoric uncertainty. 
% Methods for estimating epistemic uncertainty include Bayesian neural networks \cite{mackay_practical_1992, neal_bayesian_1995}, ensembling \cite{gal_dropout_2016,lakshminarayanan_simple_2017} and a suite of recent research into out-of-distribution detection (see \cref{sec:out-of-distribution-detection}). 
In contrast to aleatoric uncertainty, which is usually represented by a distribution over the data, epistemic uncertainty is often represented by an implicit or explicit distribution over the model parameters, such as in Bayesian neural networks \cite{mackay_practical_1992, neal_bayesian_1995} and ensemble models \cite{gal_dropout_2016,lakshminarayanan_simple_2017}. In most cases, such methods require multiple forward passes through the model to estimate the predictive uncertainty making them computationally expensive and impractical for real-time applications. Within the field of out-of-distribution detection, the epistemic uncertainty is generally not expressed in model parameters, but e.g. by a distribution over data representations, output probabilities with special classes for out-of-distribution data, or by distances in feature spaces. In such cases, the uncertainty can often be estimated in a single forward pass through the model.
